---
title: "R Notebook"
output: html_notebook
---

Plan


Start with Iron Maiden

You will want to compare some albums. Maybe just discography?

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
iron_maiden_lyrics <- read_csv("iron_maiden_lyrics.csv")

```


```{r}
playlist3 <- get_playlist_audio_features("b7iflt2s6um28zx952r2rp1q9","12fnBe9fV0JvVtSg3SPSmW")

maiden_all <- playlist3 %>%
  dplyr::select(track.artists, track.name, track.popularity, track.album.name, danceability, energy, key, loudness, mode, speechiness, acousticness, instrumentalness, valence, tempo, time_signature, track.duration_ms, key_name, mode_name, key_mode, track.id, track.album.id, track.album.release_date, track.album.release_date_precision)

maiden_all <- maiden_all %>%
  dplyr::rename(artist = track.artists) %>%
  dplyr::rename(track = track.name) %>%
  dplyr::rename(popularity = track.popularity) %>%
  dplyr::rename(album_name = track.album.name) %>%
  dplyr::rename(duration_ms = track.duration_ms) %>%
  dplyr::rename(track_id = track.id) %>%
  dplyr::rename(album_id = track.album.id) %>%
  dplyr::rename(album_release_date = track.album.release_date) %>%
  dplyr::rename(album_release_date_precision = track.album.release_date_precision)

maiden_all1 <- maiden_all %>%
  dplyr::mutate(across("track", str_replace, "- 2015 Remaster", ""))
```
- 2015 Remaster
dplyr::mutate(across("track", str_replace, "- 2015 Remaster", ""))

dplyr::union(iron_maiden_lyrics$track, maiden_all2$track)

#Lyrics
```{r}
iron_maiden_lyrics <- iron_maiden_lyrics %>%
  dplyr::rename(track = musica) %>%
  dplyr::rename(lyrics = letras)
```

album_name contains remaster

```{r}
maiden_all2 <- maiden_all1 %>%
  dplyr::filter(album_name %in% str_subset(album_name, "Remaster")) %>%
  mutate(across(track, str_trim))
```

mutate(across(where(is.character), str_trim))
mutate(across(where(is.character), str_trim))
mutate(across(track, str_trim))


str_replace_all(x, fixed(" "), "")

```{r}
dplyr::union(iron_maiden_lyrics$track, maiden_all2$track)

maiden_all2$track <- str_trim(maiden_all2$track, side = "right")

#Get both in the same format

iron_maiden_lyrics <- iron_maiden_lyrics %>%
  dplyr::mutate(across("track", stringr::str_to_title))

maiden_all2 <- maiden_all2 %>%
  dplyr::mutate(across("track", stringr::str_to_title))

test <- dplyr::union(iron_maiden_lyrics$track, maiden_all2$track)
```

```{r}
iron_maiden_lyrics <- iron_maiden_lyrics %>%
  dplyr::distinct(track, .keep_all = TRUE)

iron_maiden_lyrics1 <- iron_maiden_lyrics
```

```{r}
iron_maiden_lyrics <- iron_maiden_lyrics %>%
  dplyr::mutate(across("track", str_replace, "2 A.m.", "2 Am"))

iron_maiden_lyrics <- iron_maiden_lyrics %>%
  dplyr::filter(!grepl(remove_songs1, track)) %>%
  dplyr::arrange(track)



remove_songs <- paste(c("Churchill's Speech","Cross-Eyed Mary","Virus","Total Eclipse","Sanctuary","Massacre","Intro: Churchill's Speech","Intro: Aces High"))
remove_songs1 <- paste(c("Churchill's Speech","Cross-Eyed Mary","Virus","Total Eclipse","Sanctuary","Massacre","Intro: Churchill's Speech","Intro: Aces High"), collapse = '|')      
  

```

```{r}
maiden_all3 <- maiden_all2 %>%
  dplyr::mutate(across("track", str_replace, "\\(", "")) %>%
  dplyr::mutate(across("track", str_replace, "\\)", "")) %>%
  dplyr::mutate(across("track", str_replace, "356-323 B.c.", "")) %>%
  dplyr::mutate(across("track", str_replace, "Satellite 15.....The Final Frontier", "Satellite 15... The Final Frontier"))

maiden_all3 <- maiden_all3 %>%
  dplyr::arrange(track)
```

Cbind
```{r}
combined <- maiden_all3 %>%
  add_column(iron_maiden_lyrics$lyrics)

write_csv(combined1, "iron_maiden_audio_plus_lyrics.csv")
```

```{r}
combined1 <- combined1 %>%
  dplyr::select(-artist) 



```

