---
title: "R Notebook"
output: html_notebook
---

Taylor info lol

#for later
taylor_with_lyrics <- read_csv("~/Downloads/tayloR-master/taylor_with_lyrics.csv")

```{r}
## Get data
taylor <- get_artist_audio_features('taylor swift')

# Reorder columns 
taylor <- taylor %>%
  dplyr::relocate(album_name, .before = artist_id) %>%
  dplyr::relocate(track_name, .before = artist_name)

#View the album names so you can remove the ones you don't want
taylor %>%
  dplyr::distinct(album_name)

#List to keep
album_list <- paste(c("Taylor Swift", "Fearless Platinum Edition", "Speak Now", "Red", "1989", "reputation", "Lover", "folklore", "evermore"))

#List of words in song titles to remove
remove_list <- paste(c("Demo Recording", "Karaoke Version", "Pop Version", "Acoustic Version", "Commentary", "Medley", "Instrumental", 
                       "Live From", "Edit", "Mix", "Radio", "Live/","Piano Version"), collapse = '|')
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

```{r}
#Create tibble
taylor_filtered <- taylor %>%
  as_tibble()

#Remove albums you don't want
taylor_filtered <- taylor_filtered %>%
  dplyr::filter(album_name %in% album_list)

#Removing songs, might want to get back to this with stringr
taylor_filtered <- taylor_filtered %>%
  filter(!grepl(remove_list, track_name))

#Removing duplicates
taylor_filtered <- taylor_filtered %>%
  dplyr::distinct(track_name, .keep_all = TRUE)
```
spotify_filt

intersect

```{r}
dplyr::intersect(spotify_filt$name, taylor_filtered$track_name)
```


```{r}
#fixing the album name
taylor_filtered <- taylor_filtered %>%
  dplyr::mutate(across("album_name", str_replace, "Fearless Platinum Edition", "Fearless"))

#checking if it worked
taylor_filtered %>%
  dplyr::distinct(album_name)

#Not all the album names are in the same format, capitalising them

taylor_filtered <- taylor_filtered %>%
  dplyr::mutate(across("album_name", stringr::str_to_title))

#The same with song titles
taylor_filtered <- taylor_filtered %>%
  dplyr::mutate(across("track_name", stringr::str_to_title))

```


```{r}
#check for missing data
sum(is.na(taylor_filtered))

#remove track_preview_url since we don't need it anyway
taylor_filtered <- taylor_filtered %>%
  dplyr::select(-track_preview_url)

sum(is.na(taylor_filtered))
```


#Track pop
```{r}
spotify1 <- read_csv("~/Downloads/19332_Spotify_Songs.csv")
spotify2 <- read_csv("~/Downloads/data.csv")
spotify3 <- read_csv("~/Downloads/Master Song CSV.csv")
spotify4 <- read_csv("~/Downloads/archive/data.csv")
spotify5 <- read_csv("~/Downloads/spotify_songs.csv")
```

```{r}
#This has it mixed in the artists column
dim(spotify1)
head(spotify1)

spotify1 %>%
  dplyr::filter(artists %in% str_subset(artists, "Taylor Swift")) %>%
  dplyr::distinct(name)

#101
###

dim(spotify2)
head(spotify2)

spotify2_filt <- spotify2 %>%
  dplyr::filter(artists %in% str_subset(artists, "Taylor Swift")) %>%
  dplyr::distinct(name, .keep_all = TRUE)

dim(spotify4)
head(spotify4)

spotify4_filt <- spotify4 %>%
  dplyr::filter(artists %in% str_subset(artists, "Taylor Swift")) %>%
  dplyr::distinct(name, .keep_all = TRUE)

spotify_filt <- bind_rows(spotify2_filt, spotify4_filt) %>% #because of this I can use distinct. union would work if I didn't combine it
  dplyr::distinct(name, .keep_all = TRUE)

dplyr::union(spotify4_filt$name, spotify2_filt$name) #this does the same, but would only save it as a vector
  
```





```{r}
spotify_filt <- spotify_filt %>%
  dplyr::mutate(artists = str_replace_all(artists, "\\'|\\[|\\]", ""))

spotify_filt <- spotify_filt %>%
  dplyr::relocate(artists, .before = acousticness) %>%
  dplyr::relocate(name, .before = artists) 

#Need to add column for album, do it by year?  

spotify_filt <- spotify_filt %>%
  dplyr::filter(!grepl(remove_list, name))
```

```{r}
#Save in case

sub6 <- str_subset(spotify6$artists, "Taylor Swift")
dplyr::filter(artists %in% sub6)
```


E

```{r}

tay_playlist <- get_playlist_audio_features("b7iflt2s6um28zx952r2rp1q9", "5MhycXBWZlAbAKSot7d0Xe")

swift_bind2

tay_playlist1 <- tay_playlist %>%
  dplyr::select(track.name, track.popularity) %>%
  dplyr::mutate(artists = "Taylor Swift")


```

